Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-27 methods_paper/fabl-paper.tex
minor.

\cite{jaro1989} proposed addressing this issue via an optimization approach as follows:
\begin{align}
\label{eqn:jaro}
&\max_{\Delta} \sum_{i=1}^{n_1} \sum_{j=1}^{n_2} w_{ij} \Delta_{ij} 
\quad \text{subject to} \quad \Delta_{ij} \in \{0,1\};\\
& \quad \quad \sum_{i=1}^{n_1}  \Delta_{ij}  \leq 1, j=1,2, \ldots n_2; \; \text{and} \notag\\
& \quad \quad\sum_{i=1}^{n_2}  \Delta_{ij}  \leq 1, j=1,2, \ldots n_1. \notag \\
\end{align}

Equation \label{eqn:jaro} ensures that each record of $\bm{X}_2$ only matches with at most one record in $\bm{X}_1$ (and the reverse condition). This is commonly known as the \emph{maximum-weight bipartite matching problem} or a \emph{linear sum assignment problem}. The output of this algorithm is a bipartite matching that maximizes the sum of the weights among matched pairs, where the pairs are not matched are assumed to be non-matches. \cite{jaro1989} provided no theoretical justification for using this approach, however, \cite{} recently showed that under certain conditions, equation \ref{eqn:jaro} is the maximum likelihood estimate.

>>>>

\cite{jaro1989} proposed addressing this issue via an optimization approach as follows:
\begin{align}
\label{eqn:jaro}
&\max_{\Delta} \sum_{i=1}^{n_1} \sum_{j=1}^{n_2} w_{ij} \Delta_{ij} 
\quad \text{subject to} \quad \Delta_{ij} \in \{0,1\}; \\
& \quad \quad \sum_{i=1}^{n_1}  \Delta_{ij}  \leq 1, j=1,2, \ldots n_2; \; \text{and} \notag\\
& \quad \quad\sum_{i=1}^{n_2}  \Delta_{ij}  \leq 1, j=1,2, \ldots n_1. \notag
\end{align}

Equation \ref{eqn:jaro} ensures that each record of $\bm{X}_2$ only matches with at most one record in $\bm{X}_1$ (and the reverse condition). This is commonly known as the \emph{maximum-weight bipartite matching problem} or a \emph{linear sum assignment problem}. The output of this algorithm is a bipartite matching that maximizes the sum of the weights among matched pairs, where the pairs are not matched are assumed to be non-matches. \cite{jaro1989} provided no theoretical justification for using this approach, however, \cite{sadinle_bayesian_2017} recently showed that under certain conditions, equation \ref{eqn:jaro} is the maximum likelihood estimate.
